---
title: "Titanic Data"
author: "Charles Hall"
date: "May 17, 2016"
output: html_document
---

0: Load the data in RStudio

Load tidyr abd dplyr. Read the csv and convert blanks to proper NA values.

```{r}
library(tidyr)
library(dplyr)

ti_tanic <- read.csv("c:/Users/CMH/Desktop/DataScience/springboard/Chapter3/titanic/titanic_original.csv", header=T, na.strings=c(""," ","NA"))
ti_tanic <- tbl_df(ti_tanic)
```

1: Port of embarkation
Convert all <NA> values to S. 
```{r}
ti_tanic$embarked[is.na(ti_tanic$embarked)] <- c("S")
```

2: Age
Replace missing ages with the mean age.
I would consider a regression or something similar to find a better age replacement.
I would also consider the cabin and sex. eg. Partner or child.
```{r}
ti_tanic$age[is.na(ti_tanic$age)] <- mean(ti_tanic$age, na.rm=TRUE)
```

3: Lifeboat
I do not run this command because the na.strings in the read.csv converts these to R <NA> values,
which I believe could bemore useful. I inclded this line in the interest of completeness.
```{r}
#ti_tanic$boat[is.na(ti_tanic$boat)] <- c("None")
```

4: Cabin
```{r}
ti_tanic <- ti_tanic %>%
  mutate(has_cabin_number = !is.na(ti_tanic$boat))
```

6: Submit the project on Github
This should probably be 5
```{r}
write.csv(to_refine, file = "c:/Users/CMH/Desktop/DataScience/springboard/Chapter3/titanic/titanic_clean.csv")
```